A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add ZBDD description

>>>>

This representation is especially useful when the data can be represented as
(sparse) bit vectors. Any subset of these bit vectors can be represented by a
Boolean function over $n$ variables. If the corresponding bit vector is in the
set, the \textit{Zero-Suppressed BDDs} (\textit{ZBDDs}) yields 1 for a given
variable assignment.

The bit vector are \textit{sparse} in the sense that the set contains much less
than $2^n$ vectors and the bit vectors themselves have many zero elements. ZBDDs
are similar to OBDDs but they use a different reduction rule, exploiting the
sparse bit vectors. In ZBDDs, nodes can be eliminated whenever setting the
corresponding variable to 1 yields 0 as result, which is often the case for sparse
bit vectors. This representation proved successful to solve some combinatorial
problems~\cite{BRYANT95}. \tbr
